Scheduling and Amortization for MPC

### 2022-02-16 paper_SIMD.tex
Edits to Demensionality reduction.

>>>>

\COMMENT {Phase 4: Dimensionality reduction: remove unnecessary dimensionality. \ana{Better draft! Needs a bit more work.}}

\COMMENT { A dimension i is dead on exit from stmt v[...i...] = ... if all def-uses with targets outside of the enclosing 
FOR i=0 ... MOTION loop end at target (use) v' = drop\_dim(v, i). } 
\FOR {each stmt and dimension v[...i...] = ...}
\STATE {if i is a dead dimension on exit from stmt v[...i...] = ..., remove i from v[...i...] (at def and at all uses)} 
%\COMMENT{ A stmt v[...i] is a "dead dimension i" if all edges out of FOR i = 0; ... loop end at drop\_dim(v, i)}
\ENDFOR

\COMMENT {Now clean up drop\_dim and raise\_dim}
\FOR {each v' =  drop\_dim(v,i) }
\STATE {replace with v' = v if i is dead in v.}
\ENDFOR
\FOR {each v' = raise\_dim(v,i) in outer loop to use: v'[...i...] in loop}
\STATE {replace v' with v in use statement}
\ENDFOR
\STATE {do copy propagation and dead code elimination to get rid of redundant variables and raise dimension statements}
